Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-04-19 products/manuscript/Manuscript.qmd
summary table caption

After deciding on a single outcome variable, we created a summary table with that outcome and the seven predictors we will use to predict it, which can be seen in @tbl-1. [insert explanation here]
```{r}
#| message: false
#| label: tbl-1
#| tbl-cap: "Summary Table Of Continuous Variables by Region"
#| echo: FALSE
predictortable<- readRDS(here("results", "tables", "predictortable.rds"))
predictortable
```

>>>>

After deciding on a single outcome variable, we created a summary table with that outcome and the seven predictors we will use to predict it, which can be seen in @tbl-1. [insert explanation here]
```{r}
#| message: false
#| label: tbl-1
#| tbl-cap: "[A summary table was done to present data about the seven predictor variables chosen in a structured format. Summary tables enable us to compare between different categories or groups within the data set. This can reveal trends or relationships. From the summary table below, it would appear that] Latin America/the Caribbean has the highest percentage of unintended pregancies due to SARC usage."
#| echo: FALSE
predictortable<- readRDS(here("results", "tables", "predictortable.rds"))
predictortable
```
